---
title: "Final_Project"
output:
  pdf_document: default
  html_document:
    df_print: paged
date: "2024-11-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Problem Statement:-**

You have been assigned the task of forming groups. Consider that your class consists of 15 students, and you aim to create 5 groups, each containing 3 students. The main goal is to maximize the chance of success for each group on a class project. The requirements for forming groups are as follows:\
• Divide 15 students into 5 groups of 3 members each.\
• What factors affect the success of groups? Define three factors (e.g., GPA, gender, etc…)that you feel influence the contributions students make towards project success.\
• Use R’s randomization function to generate data for these factors.\
• Record the collected data.\
• Formulate a mathematical model with an objective function, constraints, and non-negativity components.\
• Solve the model in R and report objective function values and decision variables.\
• Provide insights in your results.

**Solution:-**

The goal is to create five groups for a project by systematically allocating 15 students according to their unique characteristics.\
The factors influencing the categorisation of students into distinct groups are as follows:

**The Student's GPA:**\
This metric indicates the average performance of a student across their academic courses. This metric effectively quantifies a student's comprehensive performance in their academic pursuits and offers valuable insights into their educational status. The student’s quality and capabilities are effectively highlighted, contributing significantly to the project’s success.

**Technical Proficiency:**\
Technical skills reflect a student's expertise in particular technical domains pertinent to the project. These skills demonstrate their capacity to contribute efficiently and execute tasks that necessitate specialized knowledge.

**Collaboration:**\
This aspect demonstrates a student's capacity to work alongside peers, share duties, and enhance the overall dynamics of the group. This reflects a student's ability to collaborate effectively with peers to reach shared objectives, promoting a cooperative and efficient group setting.

Percentage (out of 100) of the elements that contributed to the success of the group project:

1. The student's GPA is 40%.\
2. Skill Level: 30%\
3. Collaboration: 30 Percent\

**Employing R's randomization function to produce data for these factors**
```{r}
set.seed(123)
num_rows <- 15

GPA <- round(runif(num_rows, min = 2.5, max = 4.0),2)
gpa_data <- data.frame(GPA = GPA)

Technical_proficiency_scale <- round(runif(num_rows, min = 4, max = 10),0)
gpa_data <- data.frame(Technical_proficiency_scale = Technical_proficiency_scale)

Collaboration_scale <- round(runif(num_rows, min = 4, max = 10),0)
gpa_data <- data.frame(Collaboration_scale = Collaboration_scale)

GPA_mean <- mean(GPA)
round(GPA_mean,2)
```

```{r}
Technical_proficiency_mean <- mean(Technical_proficiency_scale)
round(Technical_proficiency_mean,0)
```

```{r}
Collaboration_mean <- mean(Collaboration_scale)
round(Collaboration_mean,0)
```
# Factor Distributions
```{r factor-distribution, echo=FALSE, fig.width=10, fig.height=4}
par(mfrow = c(1, 3), mar = c(4, 4, 2, 1))  # Adjust layout and margins
# GPA Distribution
hist(GPA, 
     breaks = 10, 
     col = "skyblue", 
     main = "GPA Distribution", 
     xlab = "GPA", 
     ylab = "Frequency", 
     cex.main = 1.5, 
     cex.lab = 1.2, 
     cex.axis = 1.1, 
     border = "darkblue")
grid(nx = NULL, ny = NULL, col = "gray", lty = "dotted")

# Technical Proficiency Scale Distribution
hist(Technical_proficiency_scale, 
     breaks = 7, 
     col = "mediumorchid", 
     main = "Technical Proficiency Distribution", 
     xlab = "Score", 
     ylab = "Frequency", 
     cex.main = 1.5, 
     cex.lab = 1.2, 
     cex.axis = 1.1, 
     border = "darkorchid4")
grid(nx = NULL, ny = NULL, col = "gray", lty = "dotted")

# Collaboration Scale Distribution
hist(Collaboration_scale, 
     breaks = 7, 
     col = "tomato", 
     main = "Collaboration Distribution", 
     xlab = "Score", 
     ylab = "Frequency", 
     cex.main = 1.5, 
     cex.lab = 1.2, 
     cex.axis = 1.1, 
     border = "darkred")
grid(nx = NULL, ny = NULL, col = "gray", lty = "dotted")

```
# Visualization for GPA distribution
```{r}
library(ggplot2)

ggplot(gpa_data, aes(x = GPA)) +
  geom_histogram(binwidth = 0.1, fill = "blue", color = "black", alpha = 0.8) +  # Adjust opacity for clearer view
  labs(
    title = "Distribution of GPA", 
    x = "GPA", 
    y = "Frequency"
  ) +
  theme_minimal() +  # Use a clean, minimalist theme
  theme(
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),  # Center and bold the title
    axis.title = element_text(size = 14),                             # Larger axis titles
    axis.text = element_text(size = 12)                               # Larger tick labels
  ) +
  scale_x_continuous(breaks = seq(0, 4, by = 0.2))  # Custom x-axis breaks for precision

```
**Creating a Table**
```{r}
library(kableExtra, warn.conflicts = FALSE)
Student <- c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","Avg")
GPA_Value <- c(GPA, 3.35)
Technical_proficiency_scale_Value <- c(Technical_proficiency_scale, 7)
Collaboration_scale_value <- c(Collaboration_scale, 7)

Student_data <- data.frame(Student,GPA_Value, Technical_proficiency_scale_Value, Collaboration_scale_value)

gpa_weight <- 0.4
Technical_proficiency_weight <- 0.3
Collaboration_weight <- 0.3

Student_data$Weighted_Avg <- round((Student_data$GPA_Value * gpa_weight +
                        Student_data$Technical_proficiency_scale_Value * Technical_proficiency_weight +
                        Student_data$Collaboration_scale_value * Collaboration_weight),2)

Student_data %>%
  kable(align = "c", format = "latex") %>%
  kable_styling(bootstrap_options = "bordered", full_width = TRUE) %>%
  row_spec(16,bold = TRUE)%>%
    row_spec(15,extra_css = "border-bottom:dotted;")%>%
add_header_above(c("Factors Contributing for Success of the Group" = 5))
```
# Weighted Averages
```{r}
library(ggplot2)

# Create bar chart
ggplot(Student_data, aes(x = reorder(Student, -Weighted_Avg), y = Weighted_Avg)) +  # Sort in descending order
  geom_bar(stat = "identity", fill = "darkblue", width = 0.7) +                     # Adjust bar width
  geom_text(aes(label = round(Weighted_Avg, 2)),                                   # Add labels on bars
            hjust = -0.2, size = 3, color = "black") +                             # Adjust position and size
  coord_flip() +                                                                   # Flip axes for horizontal bars
  labs(title = "Weighted Average Scores by Student", 
       x = "Student", 
       y = "Weighted Average") +                                                   # Add axis labels
  theme_light() +                                                                  # Use light theme
  theme(
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),              # Title styling
    axis.text.y = element_text(size = 10),                                         # Student labels
    axis.text.x = element_text(size = 10),                                         # Weighted Average axis
    axis.title = element_text(size = 12)                                          # Axis titles
  )

```
**Developing the Model:**\
Identifying the decision variables, establishing the objective function, and outlining the constraints according to the specified requirements and initial concerns.\
Prior to delving into the formulation, it is essential to establish the decision variables, which will be discussed in the following sections.\
$G_{i}$ represent groups where i=1,2,3,4,5\
$S_{j}$ represents students where j=1,2,3,4,5,6,7,8,9,10,11,12,13,14,15

**Objective function:-**\
The main objective is to enhance the success of the group in a class project by considering three key factors: GPA, technical proficiency, and collaboration. The identified factors that influence student contributions to project success have been assigned weights reflecting their respective impacts: GPA accounts for 40%, Technical Proficiency for 30%, and Collaboration for 30%. To formulate the objective function, we calculated the weighted average of the three factors. The resulting objective function can be expressed as follows:

Max Z= $6.87G_{1}S_{1}+5.67G_{1}S_{2}+4.84G_{1}S_{3}+6.03G_{1}S_{4}+5.76G_{1}S_{5}+5.83G_{1}S_{6}+6.42G_{1}S_{7}+5.44G_{1}S_{8}+6.13G_{1}S_{9}+5.17G_{1}S_{10}+5.48G_{1}S_{11}+5.17G_{1}S_{12}+5.61G_{1}S_{13}+4.94G_{1}S_{14}+4.06G_{1}S_{15}+6.87G_{2}S_{1}+5.67G_{2}S_{2}+4.84G_{2}S_{3}+6.03G_{2}S_{4}+5.76G_{2}S_{5}+5.83G_{2}S_{6}+6.42G_{2}S_{7}+5.44G_{2}S_{8}+6.13G_{2}S_{9}+5.17G_{2}S_{10}+5.48G_{2}S_{11}+5.17G_{2}S_{12}+5.61G_{2}S_{13}+4.94G_{2}S_{14}+4.06G_{2}S_{15}+6.87G_{3}S_{1}+5.67G_{3}S_{2}+4.84G_{3}S_{3}+6.03G_{3}S_{4}+5.76G_{3}S_{5}+5.83G_{3}S_{6}+6.42G_{3}S_{7}+5.44G_{3}S_{8}+6.13G_{3}S_{9}+5.17G_{3}S_{10}+5.48G_{3}S_{11}+5.17G_{3}S_{12}+5.61G_{3}S_{13}+4.94G_{3}S_{14}+4.06G_{3}S_{15}+6.87G_{4}S_{1}+5.67G_{4}S_{2}+4.84G_{4}S_{3}+6.03G_{4}S_{4}+5.76G_{4}S_{5}+5.83G_{4}S_{6}+6.42G_{4}S_{7}+5.44G_{4}S_{8}+6.13G_{4}S_{9}+5.17G_{4}S_{10}+5.48G_{4}S_{11}+5.17G_{4}S_{12}+5.61G_{4}S_{13}+4.94G_{4}S_{14}+4.06G_{4}S_{15}+6.87G_{5}S_{1}+5.67G_{5}S_{2}+4.84G_{5}S_{3}+6.03G_{5}S_{4}+5.76G_{5}S_{5}+5.83G_{5}S_{6}+6.42G_{5}S_{7}+5.44G_{5}S_{8}+6.13G_{5}S_{9}+5.17G_{5}S_{10}+5.48G_{5}S_{11}+5.17G_{5}S_{12}+5.61G_{5}S_{13}+4.94G_{5}S_{14}+4.06G_{5}S_{15}$

**Constraints:-**\
Establishing the constraints based on all the decision variables

**Group Constraints:-**

**Students of Group 1:**\
$G_{1}S_{1}+G_{1}S_{2}+G_{1}S_{3}+G_{1}S_{4}+G_{1}S_{5}+G_{1}S_{6}+G_{1}S_{7}+G_{1}S_{8}+G_{1}S_{9}+G_{1}S_{10}+G_{1}S_{11}+G_{1}S_{12}+G_{1}S_{13}+G_{1}S_{14}+G_{1}S_{15}=3$\
**Students of Group 2:**\
$G_{2}S_{1}+G_{2}S_{2}+G_{2}S_{3}+G_{2}S_{4}+G_{2}S_{5}+G_{2}S_{6}+G_{2}S_{7}+G_{2}S_{8}+G_{2}S_{9}+G_{2}S_{10}+G_{2}S_{11}+G_{2}S_{12}+G_{2}S_{13}+G_{2}S_{14}+G_{2}S_{15}=3$\
**Students of Group 3:**\
$G_{3}S_{1}+G_{3}S_{2}+G_{3}S_{3}+G_{3}S_{4}+G_{3}S_{5}+G_{3}S_{6}+G_{3}S_{7}+G_{3}S_{8}+G_{3}S_{9}+G_{3}S_{10}+G_{3}S_{11}+G_{3}S_{12}+G_{3}S_{13}+G_{3}S_{14}+G_{3}S_{15}=3$\
**Students of Group 4:**\
$G_{4}S_{1}+G_{4}S_{2}+G_{4}S_{3}+G_{4}S_{4}+G_{4}S_{5}+G_{4}S_{6}+G_{4}S_{7}+G_{4}S_{8}+G_{4}S_{9}+G_{4}S_{10}+G_{4}S_{11}+G_{4}S_{12}+G_{4}S_{13}+G_{4}S_{14}+G_{4}S_{15}=3$\
**Students of Group 5:**\
$G_{5}S_{1}+G_{5}S_{2}+G_{5}S_{3}+G_{5}S_{4}+G_{5}S_{5}+G_{5}S_{6}+G_{5}S_{7}+G_{5}S_{8}+G_{5}S_{9}+G_{5}S_{10}+G_{5}S_{11}+G_{5}S_{12}+G_{5}S_{13}+G_{5}S_{14}+G_{5}S_{15}=3$\

**Student Constraints:-**

**Student1:**\
$G_{1}S_{1}+G_{2}S_{1}+G_{3}S_{1}+G_{4}S_{1}+G_{5}S_{1}=1$\
**Student2:**\
$G_{1}S_{2}+G_{2}S_{2}+G_{3}S_{2}+G_{4}S_{2}+G_{5}S_{2}=1$\
**Student3:**\
$G_{1}S_{3}+G_{2}S_{3}+G_{3}S_{3}+G_{4}S_{3}+G_{5}S_{3}=1$\
**Student4:**\
$G_{1}S_{4}+G_{2}S_{4}+G_{3}S_{4}+G_{4}S_{4}+G_{5}S_{4}=1$\
**Student5:**\
$G_{1}S_{5}+G_{2}S_{5}+G_{3}S_{5}+G_{4}S_{5}+G_{5}S_{5}=1$\
**Student6:**\
$G_{1}S_{6}+G_{2}S_{6}+G_{3}S_{6}+G_{4}S_{6}+G_{5}S_{6}=1$\
**Student7:**\
$G_{1}S_{7}+G_{2}S_{7}+G_{3}S_{7}+G_{4}S_{7}+G_{5}S_{7}=1$\
**Student8:**\
$G_{1}S_{8}+G_{2}S_{8}+G_{3}S_{8}+G_{4}S_{8}+G_{5}S_{8}=1$\
**Student9:**\
$G_{1}S_{9}+G_{2}S_{9}+G_{3}S_{9}+G_{4}S_{9}+G_{5}S_{9}=1$\
**Student10:**\
$G_{1}S_{10}+G_{2}S_{10}+G_{3}S_{10}+G_{4}S_{10}+G_{5}S_{10}=1$\
**Student11:**\
$G_{1}S_{11}+G_{2}S_{11}+G_{3}S_{11}+G_{4}S_{11}+G_{5}S_{11}=1$\
**Student12:**\
$G_{1}S_{12}+G_{2}S_{12}+G_{3}S_{12}+G_{4}S_{12}+G_{5}S_{12}=1$\
**Student13:**\
$G_{1}S_{13}+G_{2}S_{13}+G_{3}S_{13}+G_{4}S_{13}+G_{5}S_{13}=1$\
**Student14:**\
$G_{1}S_{14}+G_{2}S_{14}+G_{3}S_{14}+G_{4}S_{14}+G_{5}S_{14}=1$\
**Student15:**\
$G_{1}S_{15}+G_{2}S_{15}+G_{3}S_{15}+G_{4}S_{15}+G_{5}S_{15}=1$\

**Factor constraints:-**


**GPA Constraints:**

**Group1 (Factor1):**\
$2.93G_{1}S_{1}+3.68G_{1}S_{2}+3.11G_{1}S_{3}+3.82G_{1}S_{4}+3.91G_{1}S_{5}+2.57G_{1}S_{6}+3.29G_{1}S_{7}+3.84G_{1}S_{8}+3.33G_{1}S_{9}+3.18G_{1}S_{10}+3.94G_{1}S_{11}+3.18G_{1}S_{12}+3.52G_{1}S_{13}+3.36G_{1}S_{14}+2.56G_{1}S_{15}>=3.35$\
**Group2 (Factor1):**\
$2.93G_{2}S_{1}+3.68G_{2}S_{2}+3.11G_{2}S_{3}+3.82G_{2}S_{4}+3.91G_{2}S_{5}+2.57G_{2}S_{6}+3.29G_{2}S_{7}+3.84G_{2}S_{8}+3.33G_{2}S_{9}+3.18G_{2}S_{10}+3.94G_{2}S_{11}+3.18G_{2}S_{12}+3.52G_{2}S_{13}+3.36G_{2}S_{14}+2.56G_{2}S_{15}>=3.35$\
**Group3 (Factor1):**\
$2.93G_{3}S_{1}+3.68G_{3}S_{2}+3.11G_{3}S_{3}+3.82G_{3}S_{4}+3.91G_{3}S_{5}+2.57G_{3}S_{6}+3.29G_{3}S_{7}+3.84G_{3}S_{8}+3.33G_{3}S_{9}+3.18G_{3}S_{10}+3.94G_{3}S_{11}+3.18G_{3}S_{12}+3.52G_{3}S_{13}+3.36G_{3}S_{14}+2.56G_{3}S_{15}>=3.35$\
**Group4 (Factor1):**\
$2.93G_{4}S_{1}+3.68G_{4}S_{2}+3.11G_{4}S_{3}+3.82G_{4}S_{4}+3.91G_{4}S_{5}+2.57G_{4}S_{6}+3.29G_{4}S_{7}+3.84G_{4}S_{8}+3.33G_{4}S_{9}+3.18G_{4}S_{10}+3.94G_{4}S_{11}+3.18G_{4}S_{12}+3.52G_{4}S_{13}+3.36G_{4}S_{14}+2.56G_{4}S_{15}>=3.35$\
**Group5 (Factor1):**\
$2.93G_{5}S_{1}+3.68G_{5}S_{2}+3.11G_{5}S_{3}+3.82G_{5}S_{4}+3.91G_{5}S_{5}+2.57G_{5}S_{6}+3.29G_{5}S_{7}+3.84G_{5}S_{8}+3.33G_{5}S_{9}+3.18G_{5}S_{10}+3.94G_{5}S_{11}+3.18G_{5}S_{12}+3.52G_{5}S_{13}+3.36G_{5}S_{14}+2.56G_{5}S_{15}>=3.35$\

**Technical Proficiency Constraints:**

**Group1 (Factor2):**\
$9G_{1}S_{1}+5G_{1}S_{2}+4G_{1}S_{3}+6G_{1}S_{4}+10G_{1}S_{5}+9G_{1}S_{6}+8G_{1}S_{7}+8G_{1}S_{8}+10G_{1}S_{9}+8G_{1}S_{10}+8G_{1}S_{11}+7G_{1}S_{12}+8G_{1}S_{13}+6G_{1}S_{14}+5G_{1}S_{15}>=7$\
**Group2 (Factor2):**\
$9G_{2}S_{1}+5G_{2}S_{2}+4G_{2}S_{3}+6G_{2}S_{4}+10G_{2}S_{5}+9G_{2}S_{6}+8G_{2}S_{7}+8G_{2}S_{8}+10G_{2}S_{9}+8G_{2}S_{10}+8G_{2}S_{11}+7G_{2}S_{12}+8G_{2}S_{13}+6G_{2}S_{14}+5G_{2}S_{15}>=7$\
**Group3 (Factor2):**\
$9G_{3}S_{1}+5G_{3}S_{2}+4G_{3}S_{3}+6G_{3}S_{4}+10G_{3}S_{5}+9G_{3}S_{6}+8G_{3}S_{7}+8G_{3}S_{8}+10G_{3}S_{9}+8G_{3}S_{10}+8G_{3}S_{11}+7G_{3}S_{12}+8G_{3}S_{13}+6G_{3}S_{14}+5G_{3}S_{15}>=7$\
**Group4 (Factor2):**\
$9G_{4}S_{1}+5G_{4}S_{2}+4G_{4}S_{3}+6G_{4}S_{4}+10G_{4}S_{5}+9G_{4}S_{6}+8G_{4}S_{7}+8G_{4}S_{8}+10G_{4}S_{9}+8G_{4}S_{10}+8G_{4}S_{11}+7G_{4}S_{12}+8G_{4}S_{13}+6G_{4}S_{14}+5G_{4}S_{15}>=7$\
**Group5 (Factor2):**\
$9G_{5}S_{1}+5G_{5}S_{2}+4G_{5}S_{3}+6G_{5}S_{4}+10G_{5}S_{5}+9G_{5}S_{6}+8G_{5}S_{7}+8G_{5}S_{8}+10G_{5}S_{9}+8G_{5}S_{10}+8G_{5}S_{11}+7G_{5}S_{12}+8G_{5}S_{13}+6G_{5}S_{14}+5G_{5}S_{15}>=7$\

**Collaboration Constraint:**

**Group1 (Factor3):**\
$10G_{1}S_{1}+9G_{1}S_{2}+8G_{1}S_{3}+9G_{1}S_{4}+4G_{1}S_{5}+7G_{1}S_{6}+9G_{1}S_{7}+5G_{1}S_{8}+6G_{1}S_{9}+5G_{1}S_{10}+5G_{1}S_{11}+6G_{1}S_{12}+6G_{1}S_{13}+6G_{1}S_{14}+5G_{1}S_{15}>=7$\
**Group2 (Factor3):**\
$10G_{2}S_{1}+9G_{2}S_{2}+8G_{2}S_{3}+9G_{2}S_{4}+4G_{2}S_{5}+7G_{2}S_{6}+9G_{2}S_{7}+5G_{2}S_{8}+6G_{2}S_{9}+5G_{2}S_{10}+5G_{2}S_{11}+6G_{2}S_{12}+6G_{2}S_{13}+6G_{2}S_{14}+5G_{2}S_{15}>=7$\
**Group3 (Factor3):**\
$10G_{3}S_{1}+9G_{3}S_{2}+8G_{3}S_{3}+9G_{3}S_{4}+4G_{3}S_{5}+7G_{3}S_{6}+9G_{3}S_{7}+5G_{3}S_{8}+6G_{3}S_{9}+5G_{3}S_{10}+5G_{3}S_{11}+6G_{3}S_{12}+6G_{3}S_{13}+6G_{3}S_{14}+5G_{3}S_{15}>=7$\
**Group4 (Factor3):**\
$10G_{4}S_{1}+9G_{4}S_{2}+8G_{4}S_{3}+9G_{4}S_{4}+4G_{4}S_{5}+7G_{4}S_{6}+9G_{4}S_{7}+5G_{4}S_{8}+6G_{4}S_{9}+5G_{4}S_{10}+5G_{4}S_{11}+6G_{4}S_{12}+6G_{4}S_{13}+6G_{4}S_{14}+5G_{4}S_{15}>=7$\
**Group5 (Factor3):**\
$10G_{5}S_{1}+9G_{5}S_{2}+8G_{5}S_{3}+9G_{5}S_{4}+4G_{5}S_{5}+7G_{5}S_{6}+9G_{5}S_{7}+5G_{5}S_{8}+6G_{5}S_{9}+5G_{5}S_{10}+5G_{5}S_{11}+6G_{5}S_{12}+6G_{5}S_{13}+6G_{5}S_{14}+5G_{5}S_{15}>=7$\

**Non-negativity of the decision variables:-**\
$G_{i}S_{j}$>=0 where i=1,2,3,4,5 and j=1,2,...15

Solve the Model in R: Implement the formulated model in R to find the optimal solution.

**Step 1: Loading the required libraries**
```{r}
library(lpSolveAPI)
```

**Step 2:Establishing an instance of a Linear Programming problem with 35 constraints and 75 decision variables**
```{r}
Success_Model <-make.lp(35, 75)
```

**Step 3: Establishing the coefficients of the objective function for the 75 decision variables**
```{r}
set.objfn(Success_Model, c(6.87,5.67,4.84, 6.03, 5.76, 5.83, 6.42, 5.44, 6.13, 5.17, 5.48, 5.17, 5.61, 4.94, 4.06, 
                6.87,5.67,4.84, 6.03, 5.76, 5.83, 6.42, 5.44, 6.13, 5.17, 5.48, 5.17, 5.61, 4.94, 4.06,  
                6.87,5.67,4.84, 6.03, 5.76, 5.83, 6.42, 5.44, 6.13, 5.17, 5.48, 5.17, 5.61, 4.94, 4.06,  
                6.87,5.67,4.84, 6.03, 5.76, 5.83, 6.42, 5.44, 6.13, 5.17, 5.48, 5.17, 5.61, 4.94, 4.06,  
                6.87,5.67,4.84, 6.03, 5.76, 5.83, 6.42, 5.44, 6.13, 5.17, 5.48, 5.17, 5.61, 4.94, 4.06))
```

**Step 4: Setting the objective sense to "maximum"**
```{r}
invisible(lp.control(Success_Model, sense = "max", verbose= "neutral"))
```

**Step 5: Incorporating Group Constraints to the Success_Model Problem**
```{r}
set.row(Success_Model,1, c(1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,2, c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,3, c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,4, c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,5, c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1))
```

**Step 6: Incorporating Student Constraints to the Success_Model Problem**
```{r}
set.row(Success_Model,6, c( 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,7, c( 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,8, c( 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,9, c( 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,10, c( 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,11, c( 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,12, c( 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,13, c( 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,14, c( 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,15, c(0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0))
set.row(Success_Model,16, c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0))
set.row(Success_Model,17, c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0))
set.row(Success_Model,18, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0))
set.row(Success_Model,19, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0))
set.row(Success_Model,20, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1))
```

**Step 7: Incorporating Factor constraints to the Success_Model Problem**
```{r}
#GPA (Factor_1) Constraints:-

set.row(Success_Model,21, c(2.93, 3.68, 3.11, 3.82, 3.91, 2.57, 3.29, 3.84, 3.33, 3.18, 3.94, 3.18, 3.52, 3.36, 2.65, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,22, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 2.93, 3.68, 3.11, 3.82, 3.91, 2.57, 3.29, 3.84, 3.33, 3.18, 3.94, 3.18, 3.52, 3.36, 2.65, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,23, c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 2.93, 3.68, 3.11, 3.82, 3.91, 2.57, 3.29, 3.84, 3.33, 3.18, 3.94, 3.18, 3.52, 3.36, 2.65, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,24, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 2.93, 3.68, 3.11, 3.82, 3.91, 2.57, 3.29, 3.84, 3.33, 3.18, 3.94, 3.18, 3.52, 3.36, 2.65, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,25, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 2.93, 3.68, 3.11, 3.82, 3.91, 2.57, 3.29, 3.84, 3.33, 3.18, 3.94, 3.18, 3.52, 3.36, 2.65))

#Technical Proficiency (Factor_2) Constraints:-

set.row(Success_Model,26, c(9, 5, 4, 6, 10, 9, 8, 8, 10, 8, 8, 7, 8, 6, 5, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,27, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 9, 5, 4, 6, 10, 9, 8, 8, 10, 8, 8, 7, 8, 6, 5, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,28, c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 9, 5, 4, 6, 10, 9, 8, 8, 10, 8, 8, 7, 8, 6, 5, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,29, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 9, 5, 4, 6, 10, 9, 8, 8, 10, 8, 8, 7, 8, 6, 5, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,30, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 9, 5, 4, 6, 10, 9, 8, 8, 10, 8, 8, 7, 8, 6, 5))

#Collaboration (Factor_3) Constraints:-

set.row(Success_Model,31, c(10, 9, 8, 9, 4, 7, 9, 5, 6, 5, 5, 6, 6, 6, 5, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,32, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 10, 9, 8, 9, 4, 7, 9, 5, 6, 5, 5, 6, 6, 6, 5, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,33, c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 10, 9, 8, 9, 4, 7, 9, 5, 6, 5, 5, 6, 6, 6, 5, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,34, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 10, 9, 8, 9, 4, 7, 9, 5, 6, 5, 5, 6, 6, 6, 5, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0))
set.row(Success_Model,35, c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 10, 9, 8, 9, 4, 7, 9, 5, 6, 5, 5, 6, 6, 6, 5))
```

**Step 8: Creating a vector rhs that contains the values on the right-hand side of the two constraints**
```{r}
rhs<-c(3,3,3,3,3,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,3.35,3.35,3.35,3.35,3.35,7,7,7,7,7,7,7,7,7,7)
```

**Step 9: Setting the values for the constraints on the right-hand side of the Success_Model problem**
```{r}
set.rhs(Success_Model,rhs)
```

**Step 10: Establishing the constraint types for the constraints**
```{r}
set.constr.type(Success_Model,c("=","=","=","=","=","=","=","=","=","=","=","=","=","=","=","=","=","=","=", "=",">=",">=",">=", ">=",">=",">=",">=",">=",">=",">=",">=",">=",">=",">=",">="))
```

**Step 11: Establishing explicit limits for the decision variables**
```{r}
set.bounds(Success_Model,lower = rep(0,75))
```

**Step 12: Giving names to the decision variables**
```{r}
Success_Model.colnames <- c("G1S1", "G1S2", "G1S3", "G1S4", "G1S5", "G1S6", "G1S7", "G1S8", "G1S9", "G1S10", "G1S11", "G1S12", "G1S13", "G1S14", "G1S15", "G2S1", "G2S2", "G2S3", "G2S4", "G2S5", "G2S6", "G2S7", "G2S8", "G2S9", "G2S10", "G2S11", "G2S12", "G2S13", "G2S14", "G2S15", "G3S1", "G3S2", "G3S3", "G3S4", "G3S5", "G3S6", "G3S7", "G3S8", "G3S9", "G3S10", "G3S11", "G3S12", "G3S13", "G3S14", "G3S15", "G4S1", "G4S2", "G4S3", "G4S4", "G4S5", "G4S6", "G4S7", "G4S8", "G4S9", "G4S10", "G4S11", "G4S12", "G4S13", "G4S14", "G4S15", "G5S1", "G5S2", "G5S3", "G5S4", "G5S5", "G5S6", "G5S7", "G5S8", "G5S9", "G5S10", "G5S11", "G5S12", "G5S13", "G5S14", "G5S15")
```

**Step 13: Giving names to the constraints**
```{r}
Success_Model.rownames <- c("Group1Students", "Group2Students", "Group3Students", "Group4Students", "Group5Students", "Student1", "Student2", "Student3", "Student4", "Student5", "Student6", "Student7", "Student8", "Student9", "Student10","Student11","Student12", "Student13", "Student14", "Student15", "Group1Factor1", "Group2Factor1", "Group3Factor1","Group4Factor1", "Group5Factor1", "Group1Factor2","Group2Factor2","Group3Factor2","Group4Factor2", "Group5Factor2", "Group1Factor3","Group2Factor3","Group3Factor3","Group4Factor3", "Group5Factor3")
dimnames(Success_Model) = list(Success_Model.rownames,(1:75))
```

**Step 14: Setting type for the variables to ‘Integer’**
```{r}
set.type(Success_Model,1:75,type = "integer")
Success_Model
```

**Step 15: Solving the Success_Model problem with the objective function and constraints that have been specified**
```{r}
solve(Success_Model)
```

**Step 16: Obtaining the optimal objective value of the Success_Model problem**
```{r}
get.objective(Success_Model)
```

**Step 17: Obtaining the values of the decision variables at the optimal solution**
```{r}
get.variables(Success_Model)
```

**Step 18: Obtaining the values of the constraints at the optimal solution**
```{r}
get.constraints(Success_Model)
```












